Mirror, mirror on the wall. Which's the best match of them all?

### 2024-01-19 PNAS/index.Rnw
Fix probability calcs
Notation update to E_n

If we begin by considering the minimal $\ell/d$ independent comparisons between a blade cut and a wire, we can compute the overall false positive rate for all comparisons using $e$, the false positive rate for one comparison, and simple probability calculations. Let $$F_n:=\{\text{at least one false pos. in }n\text{ disjoint comparisons}\}.$$ Then, $P(F_1) = e$, $P(\overline{F_1}) = 1-e$, $P(F_n) = [1-e]^n$, and $P(\overline{F_n}) = 1 - \left[P(\overline{F_1})\right]^n$.
% Using this relationship between $F_n$ and the false positive rate $r$, we can determine what $e$ must be in order to limit $P(F_n)$ to an acceptable level by solving for $e$: $e = 1 - \left[1 - P(F_n)\right]^{1/n}$.
\Cref{fig:Accuracy} shows $P(\overline{F_n})$ on the y-axis; if 90\% is an acceptable examination-wide false positive rate (FPR), 2 comparisons can be made when the single-comparison FPR is 0.05; this increases to 10 comparisons at 0.01. Thus, at an error rate of \Sexpr{sprintf("%.2f", fpr)}, examiners can conduct approximately 5 comparisons without exceeding the examination-wide FPR of 10\%.

>>>>

If we begin by considering the minimal $\ell/d$ independent comparisons between a blade cut and a wire, we can compute the overall false positive rate for all comparisons using $e$, the false positive rate for one comparison, and simple probability calculations.
Let $$E_n:=P\left(\{\geq 1\text{ false pos. in }n\text{ disjoint comparisons}\}\right).$$
Then, $E_1 = e$, $\overline{E_1} = 1-e$, $\overline{E_n} = \left[\overline{E_1}\right]^n$, and $E_n = 1 - \overline{E_n} = 1 - [1-e]^n$.
% Using this relationship between $n$ and the false positive rate $e$, we can determine what $e$ must be in order to limit $E_n$ to an acceptable level by solving for $e$: $e = 1 - \left[1 - E_n\right]^{1/n}$.
\Cref{fig:Accuracy} shows $E_n$ on the y-axis; if 90\% is an acceptable examination-wide false positive rate (FPR), 2 comparisons can be made when the single-comparison FPR is 0.05; this increases to 10 comparisons at 0.01. Thus, at an error rate of \Sexpr{sprintf("%.2f", fpr)}, examiners can conduct approximately 5 comparisons without exceeding the examination-wide FPR of 10\%.
